MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
working on w/L criteria

for (i in 1:(ncol(ky) - 1)){
  ky[, i] <- as.character(ky[, i])
  for (j in 1:nrow(ky)){
    if (ky[j, i] == "Strongly Agree") ky[j, i] <- 5
    if (ky[j, i] == "Agree") ky[j, i] <- 4
    if (ky[j, i] == "Neither Agree nor Disagree") ky[j, i] <- 3
    if (ky[j, i] == "Disagree") ky[j, i] <- 2
    if (ky[j, i] == "Strongly Disagree") ky[j, i] <- 1
  }
  ky[, i] <- as.numeric(ky[, i])
}

>>>>

#for (i in 1:(ncol(ky) - 1)){
#  ky[, i] <- as.character(ky[, i])
 # for (j in 1:nrow(ky)){
  #  if (ky[j, i] == "Strongly Agree") ky[j, i] <- 5
   # if (ky[j, i] == "Agree") ky[j, i] <- 4
    #if (ky[j, i] == "Neither Agree nor Disagree") ky[j, i] <- 3
#    if (ky[j, i] == "Disagree") ky[j, i] <- 2
#    if (ky[j, i] == "Strongly Disagree") ky[j, i] <- 1
#  }
#  ky[, i] <- as.numeric(ky[, i])
#}
